Extensibility and Composability of a Multi-Stencil Domain Specific Framework

### 2017-03-07 ARTICLES/IJPP/articleR1/evaluation.tex
minor modif

In this section we propose an evaluation of the fusion optimization. From the $TSP$ tree computed by MSC it may be possible, according to some specific conditions, to merge the domain loops of some kernels, thus optimizing the use of cache memories. This kind of optimization is called a fusion and has been introduced in Section\ref{sect:fusion}. Three fusion optimizations
%\CP{les rappeler !}
%
have been formally detailed in Section~\ref{sect:fusion}. The two first ones of Figures~\ref{fig:fus1} and~\ref{fig:fus2}~\vpageref{fig:fus2} have been automatically detected by MSF in our case study (\ie the third scatter optimization of Fig.~\ref{fig:fus3} has not been detected).
%\CP{Et la troisieme ?}

>>>>

In this section we propose an evaluation of the fusion optimization. From the $TSP$ tree computed by MSC it may be possible, according to some specific conditions, to merge the domain loops of some kernels, thus optimizing the use of cache memories. This kind of optimization is called a fusion and
three fusion optimizations have been introduced in Section~\ref{sect:fusion}. Among 
%\CP{les rappeler !}
%
them, the two first ones (Figures~\ref{fig:fus1} and~\ref{fig:fus2}~\vpageref{fig:fus2}) have been automatically detected by MSF in this case study.% (the third scatter optimization of Fig.~\ref{fig:fus3} has not been detected).
%\CP{Et la troisieme ?}
